Visualize Non-Euclidean Actors Social Media via Joint Social Relationship Representations, Network Characteristics and Media Sentiments

### 2020-10-25 A-BasicCommom/CVPR2021/cvpr.tex
cvpr2021 3 papers final.

\def\cvprPaperID{6666} % \times \times \times  Enter the CVPR Paper ID here
\def\confYear{CVPR 2021}
%\setcounter{page}{4321} % For final version only

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
  For the shortest path calculation task of all nodes in networks, Alon \etal~\cite{alon1997exponent} proposed an algorithm with matrix multiplication.
  In this paper, with the distance product association law and block matrix multiplication, all-pairs shortest path algorithm has a lowered time-bound of \(O(\log{n}2n^3)\).
  The proposed all-pairs shortest path algorithm, which has an improved lower time-bound \(O(14n^3)\), leverages matrix sparseness judgment, convergence judgment, distance product with matrix multiplication, association law for distance product,
  scale-free characteristics of the social networks degrees and precision limit of floating point operations on the modern hardware.
  Tested on the movie actors' social network dataset, the algorithm has an improvement of 39\% to 36.2 times in performance on the CPU/GPU platforms comparing to Alon \etal's all-pairs shortest path algorithm.
\end{abstract}

@@

On the actors' social network, this paper implements Strassen block matrix multiplication, Copper-Winograd block matrix multiplication, and OpenBLAS matrix multiplication.
On the computer hardware, compared the $8508\times 8508$ matrix multiplication time-cost.
The block matrix multiplication based on Strassen and Coppersmith-Winograd takes 6 seconds for one iteration of matrix multiplication, and with the OpenBLAS library, it takes only 4 seconds.
The performance of optimized cache block matrix multiplication, such as the OpenBLAS matrix computation library, is higher than Strassen and Copper-Winograd block matrix multiplication algorithm.
Therefore, the distance product algorithm proposed by Zwick with OpenBLAS block matrix multiplication is better than the distance product algorithm with Strassen and Coppersmith-Winograd.

@@

Definition 1 (Outer Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m\times r}\), \(\Bbb B \in \Bbb R^{r\times n}\) and \(\Bbb C \in \Bbb R^{m\times n}\), the outer product is:
\begin{equation}
\Bbb C = \Bbb C  + \Bbb A(:,k)\bullet \Bbb B(k,:) , k \in (1,r)
\end{equation}

@@

Definition 2 (Distance Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m\times r}\), \(\Bbb B \in \Bbb R^{r\times n}\) and \(\Bbb C \in \Bbb R^{m\times n}\), the distance product is:
\begin{equation}
  \Bbb C = \min(\Bbb C, \Bbb A(:,k)\odot \Bbb B(k,:)) , k \in (1,r)
\end{equation}

Given two vectors \(\textsc x\), \(\textsc y\), and matrix \(\Bbb A\), having \(\Bbb A \in \Bbb R^{m\times n}\), \(\textsc x \in \Bbb R^{m}\) and \(\textsc y \in \Bbb R^{n}\) the distance product \(\odot\) is defined by:
\begin{equation}
a_{ij} = \min(a_{ij} , x_i + y_j), i \in (1,m), j \in (1,n)
\end{equation}
%-------------------------------------------------------------------------
\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{figure1.pdf}}
\end{center}
   \caption{Adjacent matrix, each iterations and the result matrix visualization of actors' social network. (a) initial state after each round of calculation, (b) the result matrix after the first round of calculation, (c) the result matrix of the second round of calculation, (d) the third and in the same time last round of calculation, the all-pairs nodes shortest path result matrix.}
\label{fig:short}
\end{figure*}

\subsection{Maximum Calculation}

Calculate the largest value of the square matrix element $\widetilde X$, such as the Formula (4).

@@

The calculation precision of different computer hardware complies with the IEEE floating point operation standard~\cite{ieee1985ieee},
first of all, transform the input matrix by exponential transformation, to be specific, taking the number of nodes as the base,
taking the difference between the largest value of the element $\widetilde X$ and the matrix elements as exponential, as shown in the Formula (5).
For the actors' social network with 8508 nodes, the diameter of the network does not allow to exceed 9.8 and 78.4 when calculating precision of 32-bit floating point and 64-bit floating point,
otherwise, the exponential operation on the computer platform will overflow.

@@

\subsection{Distance Product Exchange Law}

@@

Definition 3 (Result Reuse in Distance Product) According to the nature of the Equation (8), the process of calculating the shortest path iteration using the last result of distance product follows in turn, as shown in Formula (11).
The shortest path needs to be calculated $\lceil{log_2(n-1)}\rceil$ times matrix multiplication, from the Formula (10), it can be seen that $(n-1)\leq2^{\lceil{log_2(n-1)}\rceil}$ is the same as the simple shortest path matrix calculation result $L^{(n-1)}$, so there is a Formula (12).
Obviously, the result reuse method saves $n-2-\lceil{log_2(n-1)}\rceil$ times of matrix multiplication.
Observe the shortest path calculation process of the actors' social network, the adjacent matrix is shown in Figure 1-a, and the change of result in each iteration is shown in Figure 1-(b-d), the shortest path result matrix converges gradually, each element stabilizes as iterations go.

@@

\subsection{The Shortest Path Algorithm Fusing Sparseness Judgment And Convergence Judgment}

@@

This paper discussed a novel algorithm in the all-pairs shortest path computation tasks, using distance product association law.
The time-bound of Alon \etal distance product algorithm with block matrix multiplication is \(O({\log{n}2n^3\over \Bbb B})\).
To strengthen the conditions, on the scale-free social networks, for the precision limit of floating point operation on hardware, additional condition on the social network diameter is added to avoid floating point operation overflow during the calculation process.
the algorithm has lower time-bound \(O({14n^3\over \Bbb B})\).
With strengthened conditions, I proposed a novel algorithm, leveraging matrix sparseness judgment, and calculation convergence judgment.
\textbf{Power-Law} refers to the network node degrees conforming to the characteristics that social networks power-law distribution, and \textbf{Bound} refers to the limit on floating point arithmetic operations precision on hardware.
The experimental results show that \textbf{Power-LawBound} algorithm improves time performance by 39\% to 36.2 times on CPU/GPU hardware compared to Alon \etal's algorithm.

>>>>

\def\cvprPaperID{297} % \times \times \times  Enter the CVPR Paper ID here
\def\confYear{CVPR 2021}
%\setcounter{page}{4321} % For final version only

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
  For the shortest path calculation of the all-pairs nodes in networks, Alon \etal~\cite{alon1997exponent} proposed an algorithm with matrix multiplication.
  In this paper, with the distance product association law and block matrix multiplication, all-pairs shortest path algorithm has a lowered time-bound of \(O(2\log{n}n^3)\).
  The proposed all-pairs shortest path algorithm, which has an improved lower time-bound \(O(14n^3)\), leverages matrix sparseness judgment, convergence judgment, distance product with matrix multiplication, association law for distance product,
  scale-free characteristics of the social networks degrees and precision limit of floating point operations on the modern hardware.
  Tested on the movie actors' social network dataset, the algorithm has an improvement of 39\% to 36.2 times in performance on the CPU/GPU platforms comparing to Alon \etal's all-pairs shortest path algorithm.
\end{abstract}

@@

On the actors' social network, this paper implements Strassen block matrix multiplication, Copper-Winograd block matrix multiplication, and OpenBLAS matrix multiplication.
On the computer hardware, compared the $8508\times 8508$ matrix multiplication time cost.
The block matrix multiplication based on Strassen and Coppersmith-Winograd takes 6 seconds for one iteration of matrix multiplication, and with the OpenBLAS library, it takes only 4 seconds.
The performance of optimized cache block matrix multiplication, such as the OpenBLAS matrix computation library, is higher than Strassen and Copper-Winograd block matrix multiplication algorithm.
Therefore, the distance product algorithm proposed by Zwick with OpenBLAS block matrix multiplication is better than the distance product algorithm with Strassen and Coppersmith-Winograd.

@@

Definition 1 ($\textbf{Outer Product Matrix Multiplication}$) Given matrices \(\Bbb A \in \Bbb R^{m\times r}\), \(\Bbb B \in \Bbb R^{r\times n}\) and \(\Bbb C \in \Bbb R^{m\times n}\), the outer product is:
\begin{equation}
\Bbb C = \Bbb C  + \Bbb A(:,k)\bullet \Bbb B(k,:) , k \in (1,r)
\end{equation}

@@

Definition 2 ($\textbf{Distance Product Matrix Multiplication}$) Given matrices \(\Bbb A \in \Bbb R^{m\times r}\), \(\Bbb B \in \Bbb R^{r\times n}\) and \(\Bbb C \in \Bbb R^{m\times n}\), the distance product is:
\begin{equation}
  \Bbb C = \min(\Bbb C, \Bbb A(:,k)\odot \Bbb B(k,:)) , k \in (1,r)
\end{equation}

Given two vectors \(\textsc x\), \(\textsc y\), and matrix \(\Bbb A\), having \(\Bbb A \in \Bbb R^{m\times n}\), \(\textsc x \in \Bbb R^{m}\) and \(\textsc y \in \Bbb R^{n}\) the distance product \(\odot\) is defined by:
\begin{equation}
a_{ij} = \min(a_{ij} , x_i + y_j), i \in (1,m), j \in (1,n)
\end{equation}
%-------------------------------------------------------------------------
\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{figure1.pdf}}
\end{center}
   \caption{Visualization for each epoch: start state of adjacent matrix, iteration states, and the result states of the actors' social network.
   (a) initial state before calculation,
   (b) the result matrix of the first epoch calculation,
   (c) the result matrix of the second epoch calculation,
   (d) the third epoch of calculation, which is also the final state, that is the all-pairs nodes shortest path result matrix.}
\label{fig:short}
\end{figure*}

\subsection{Maximum Element Value Calculation}

Calculate the largest value of the square matrix element $\widetilde X$, this maximum value is latter used in the exponential computations.

@@

The precision of different computer hardware complies with the IEEE floating point operation standard~\cite{ieee1985ieee},
first of all, transform the input matrix by exponential transformation, to be specific, taking the number of nodes as the base,
taking the difference between the largest value of the element $\widetilde X$ and the matrix elements as exponential.
For the actors' social network with 8508 nodes, the diameter of the network does not allow to exceed 9.8 and 78.4 when calculating precision of 32-bit floating point and 64-bit floating point,
otherwise, the exponential operation on the computer platform will overflow.

@@

\subsection{Distance Product Association Law}

@@

Definition 3 ($\textbf{Result Reuse in Distance Product}$) According to the nature of the Equation (8), the process of calculating the shortest path iteration using the last result of distance product follows in turn, as shown in Formula (11).
The shortest path needs to be calculated $\lceil{log_2(n-1)}\rceil$ times matrix multiplication, from the Formula (10), it can be seen that $(n-1)\leq2^{\lceil{log_2(n-1)}\rceil}$ is the same as the simple shortest path matrix calculation result $L^{(n-1)}$, so there is a Formula (12).
Obviously, the result reuse method saves $n-2-\lceil{log_2(n-1)}\rceil$ times of matrix multiplication.
Observe the shortest path calculation process of the actors' social network, the adjacent matrix is shown in Figure 1-a, and the change of result in each iteration is shown in Figure 1-(b-d), the shortest path result matrix converges gradually, each element stabilizes as iterations go.

@@

\subsection{The Shortest Path Algorithm with Joint Sparseness Judgment and Convergence Judgment}

@@

This paper discussed a novel algorithm in the all-pairs shortest path computation tasks, using distance product association law.
The time-bound of Alon \etal distance product algorithm with block matrix multiplication is \(O({2\log{n}n^3\over \Bbb B})\).
To strengthen the conditions, on the scale-free social networks, for the precision limit of floating point operation on hardware,
additional condition on the social network diameter is added to avoid overflow in the floating point operations,
the analysis showed that the algorithm has a lower time-bound \(O({14n^3\over \Bbb B})\).
With a hypothesis that all the social networks have limit diameters, I proposed a novel algorithm,
which leverages matrix sparseness judgment, and calculation convergence judgment.
\textbf{Power-Law} refers to the network node degrees conforming to the characteristics that social networks power-law distribution,
and \textbf{Bound} refers to the precision limit for diameters of floating point arithmetic operations on hardware.
The experimental results show that \textbf{Power-LawBound} algorithm improves time performance by 39\% to 36.2 times
on CPU/GPU hardware compared to Alon \etal's algorithm.

### 2020-10-25 A-BasicCommom/CVPR2021/cvpr_classification.tex
cvpr2021 3 papers final.

\def\cvprPaperID{7777} % *** Enter the CVPR Paper ID here
\def\confYear{CVPR 2021}
%\setcounter{page}{4321} % For final version only

@@

  Unsupervised pre-training is important in modern research of deep learning.
  Lee \etal~\cite{lee2009convolutional} used pre-training approaches
  in Computer Vision tasks in 2009, and later from 2010 to 2016, Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary in the CV tasks,
  thus, can be omitted in some cases.
  However, it started to flourish the natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec.
  Not long before Devin \etal~\cite{devlin2019bert}'s BERT language model dominates in most frequently used tasks in natural language processing,
  which is close resemble of Vicent \etal~\cite{vincent2008extracting}'s Denoising Autoencoder model, which was initially designed for images.
  The pre-training process becomes one of the most important procedures in deep learning.

>>>>

\def\cvprPaperID{310} % *** Enter the CVPR Paper ID here
\def\confYear{CVPR 2021}
%\setcounter{page}{4321} % For final version only

@@

  Unsupervised pre-training is important to modern research of deep learning.
  Lee \etal~\cite{lee2009convolutional} used the pre-training approaches
  in Computer Vision tasks in 2009, and later from 2010 to 2016,
  Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary in the Computer Vision tasks,
  thus, can be omitted in some cases.
  However, it started to flourish the natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec.
  Not long before Devin \etal~\cite{devlin2019bert}'s BERT language model dominates in most frequently used tasks in natural language processing,
  which is close resemble of Vicent \etal~\cite{vincent2008extracting}'s Denoising Autoencoder model, which was initially designed for images.
  The pre-training process becomes one of the most important procedures in deep learning.

### 2020-10-25 A-BasicCommom/CVPR2021/cvpr_vision.tex
cvpr2021 3 papers final.

\def\cvprPaperID{8888} % *** Enter the CVPR Paper ID here
\def\confYear{CVPR 2021}
%\setcounter{page}{4321} % For final version only

@@

  In the film industry, visualizing actor stars' social media for analyzing audience intention towards movies is essential to movie producers.
  However, non-Euclidean social media is hard to analyze, I propose an FC-GRU-CNN architecture, named as \underline{N}on-\underline{E}uclidean \underline{N}et, for social media visualization.
  On the analysis of social media, social relationship representations, network characteristics and media sentiments are key factors.
  FC-GRU-CNN architecture exploits the long-term memory ability of the GRU layer in long sequences of film cast,
  the mapping ability of the CNN layer in retrieving all-pairs shortest path of the actors' social relationship,
  and non-linear capability of deep fully connected layer for movie text sentiments and other characteristics.
  The proposed model accuracy is 14\% higher than Reed \etal~\cite{reed2016learning}'s model.

@@

  With the development of social networks, actors' influence of social media is increasing, and the influence of actors' consumption spReeds through social networks,
  and using long-term social network data to study the relationships between all actors, directors, and films remains a challenge.
  It is easy to see that the relationship between box-office and the director, actors, scriptwriters, and producers are often non-linear, that is,
  it is difficult to use linear functions to build box-office prediction models.
  By analyzing the social network characteristics of movie actors, sentiments of movies in Sina Weibo posts, all-pairs shortest path,
  it is easy to get the priority of each characteristic by analysis of feature importance,
  the existing prediction algorithm only makes use of the film metadata, lacks the study on the social network characteristics of the actors,
  though the traditional explanation of the film box-office prediction algorithm is sufficing, however, the prediction accuracy is not satisfactory.
  This paper presents a model, named FC-GRU-CNN, for movie box-office prediction, combining characteristics of film metadata, actors' social network measurement,
  all-pairs shortest path, social network text sentiments, and actors' artistic contribution characteristics,
  as a result, it is 14\% higher in accuracy than Reed \etal~\cite{reed2016learning}'s model.

@@

\section{Representation Learning for Social Relationship, Network Characteristics and artisticContribution}

@@

Machine learning methods such as Linear Regression, SVN, MLP, Logistic Regression, and Na{\'i}ve Bayes cannot converge on the data set,
possibly because the sentiments on actors' social networks do not represent the commercial benefits of the film.
Actors, as creators of films, have a role to play in the box-office, but lack of other important features that also have a significant impact on the box-office,
so the machine learning fitting process can't converge in a given time.
Using the cart decision tree regression algorithm to make box-office prediction for the test set film,
the experimental results show that the prediction model has a determination coefficient of 96.05\% on the test set and 98.58\% on the training set, which is 2.87\% higher than the Qiu and Tang~\cite{qiu2018microblog} model,
and the average absolute deviation of the model is $0.1285$ million, about 28.56\% of the average box-office.
The explanation of the decision tree prediction model is more intuitive and more interpretable than linear regression, logical regression, deep neural network, and other models,
according to the prediction model structure schematic of movie box-office,
the characteristics can be sorted according to the importance, the social network structure characteristics are the most important,
the social network text sentiments characteristics, the film metadata are important, and the social network characteristics are generally important.
Compared to Qiu and Tang~\cite{qiu2018microblog}'s logistic regression model on sentiments and the determination of the coefficient of twitter index algorithm is 95.71\% ,
The model in this paper has a determination of the coefficient of 98.58\% which has a 2.87\% improvement.

\section{FC-GRU-CNN Box-Office Prediction Model}

@@

Look at the box-office distribution of $1296$ films released between 2011 and 2015,
Consider box-office forecasts as a binary classification task.
To make the data evenly distributed, the film data were pre-processed by using the median box-office of $2.635$ million as the dividing line.
So for the movies with  less than $2.635$ million box-office are classified as A-class, movies with more than $2.635$ million box-office are classified as B-class.
In the dataset division, the data were randomly selected using the $80\%:20\%$ segmentation ratio, and the training set of $1036$ films and the test set of $260$ movies were collected.
Using the actors' social network representation, the actor is quantified, that is,
the fusion of social network features, the shortest path characteristics, and the actors' artistic characteristics.
For actors without social network data, use zero-value initialization in the actor feature matrix for the unknown characteristics.
As shown in Figure 1, the model is divided into three parts:

\begin{itemize}
\item The first part is the fully connected layer, its input feature is the film metadata and movie-related Sina Weibo sentiments, in a total of 5 dimensions.
\item The second part is the GRU layer, the input feature is the actor social network measurement characteristics and artistic characteristics, the film cast is a long list,
the longest 225 actors, for less than 225 actors using the front-end padding, the GRU layer is to solve the long-term memory loss of the structure.
\item The last part is the 5 CNN layers, input from the actors' social network shortest path feature, similarly, the film cast is a long list,
input less than 225 dimensions is fulfilled by padding, CNN has a good ability to capture multi-dimensional features, and use of Max-pooling layer to solve the problem of multi-dimension feature extraction.
\end{itemize}
Finally, the three parts are merged into one layer and then connect to a Softmax layer, and the $L_2$ regularization method is adopted to avoid overfitting.

>>>>

\def\cvprPaperID{308} % *** Enter the CVPR Paper ID here
\def\confYear{CVPR 2021}
%\setcounter{page}{4321} % For final version only

@@

  In the film industry, visualizing actor stars' social media for analyzing audience intention towards movies is essential for movie producers.
  However, non-Euclidean social media is hard to analyze, I propose an FC-GRU-CNN architecture, named as \underline{N}on\underline{E}uclidean\underline{N}et, for social media visualization.
  On the analysis of social media, social relationship representations, network characteristics and media sentiments are key factors.
  The FC-GRU-CNN architecture exploits the long-term memory ability of the GRU layer in the long sequences of film cast,
  the mapping ability of the CNN layer in retrieving all-pairs shortest path of the actors' social relationship,
  and non-linear capability in deep fully connected layer for movie text sentiments and other characteristics.
  The proposed model accuracy is 14\% higher than Reed \etal~\cite{reed2016learning}'s model.

@@

  With the development of social networks, the actors' influence of social media is increasing,
  and the influence of actors' consumption spreads through social networks,
  and using the long-term social network data to study the relationships between all actors, directors, and films remains a challenge.
  It is easy to see that the relationship between the box-office and the director, actors, scriptwriters, and producers are often non-linear, that is,
  it is difficult to use linear functions to build box-office prediction models.
  By analyzing the social network characteristics of the movie actors, sentiments of movies in Sina Weibo posts, all-pairs shortest path,
  it is easy to summarize the priority of each characteristic by analysis of feature importance,
  the existing prediction algorithm only makes use of the film metadata, lacks the study on the social network characteristics of the actors,
  though the traditional explanation of the film box-office prediction algorithm is sufficing, however, the prediction accuracy is not satisfactory.
  This paper presents a model, named FC-GRU-CNN, for movie box-office prediction, combining characteristics of film metadata, actors' social network measurement,
  all-pairs shortest path, social network text sentiments, and actors' artistic contribution characteristics,
  as a result, it is 14\% higher in accuracy than Reed \etal~\cite{reed2016learning}'s model.

@@

\section{Representation Learning for Social Relationship, Network Characteristics and Artistic Contribution}

@@

Machine learning methods such as Linear Regression, SVM, MLP, Logistic Regression, and Na{\'i}ve Bayes cannot converge on the data set,
possibly because the sentiments on actors' social networks do not represent the commercial benefits of the film.
Actors, as creators of films, have a role to play in the box-office, but lack of other important features that also have a significant impact on the box-office,
so the machine learning fitting process can't converge in a given time.
Using the cart decision tree regression algorithm to make box-office prediction for the test set film,
the experimental results show that the prediction model has a determination coefficient of 96.05\% on the test set and 98.58\% on the training set, which is 2.87\% higher than the Qiu and Tang~\cite{qiu2018microblog} model,
and the average absolute deviation of the model is $0.1285$ million, about 28.56\% of the average box-office.
The explanation of the decision tree prediction model is more intuitive and more interpretable than linear regression, logical regression, deep neural network, and other models,
according to the prediction model structure schematic of movie box-office,
the characteristics can be sorted according to the importance, the social network structure characteristics are the most important,
the social network text sentiments characteristics, the film metadata are important, and the social network characteristics are generally important.
Compared to Qiu and Tang~\cite{qiu2018microblog}'s logistic regression model on sentiments and the determination of the coefficient of twitter index algorithm is 95.71\% ,
The model in this paper has a determination of the coefficient of 98.58\% which has a 2.87\% improvement.

\section{the FC-GRU-CNN Box-Office Prediction Model}

@@

Look at the box-office distribution of $1296$ films released between 2011 and 2015,
box-office forecasts can be seen as a binary classification task.
To make the data evenly distributed, the film data were pre-processed by using the median box-office of $2.635$ million as the dividing line.
So for the movies with  less than $2.635$ million box-office are classified as A-class, movies with more than $2.635$ million box-office are classified as B-class.
In the dataset division, the data were randomly selected using the $80\%:20\%$ segmentation ratio, and the training set of $1036$ films and the test set of $260$ movies were collected.
Using the actors' social network representation, the actor is quantified, that is,
the fusion of social network features, the shortest path characteristics, and the actors' artistic characteristics.
For actors without social network data, use zero-value initialization in the actor feature matrix for the unknown characteristics.
As shown in Figure 1, the model is divided into three parts:

\begin{itemize}
\item The first part is the fully connected layer, its input feature is the film metadata and movie-related Sina Weibo sentiments, in a total of 5 dimensions.
\item The second part is the GRU layer, the input feature is the actor social network measurement characteristics and artistic characteristics, the film cast is a long list,
the longest 225 actors, for less than 225 actors using the front-end padding, the GRU layer is to solve the long-term memory loss of the structure.
\item The last part is the 5 CNN layers, input from the actors' social network shortest path feature, similarly, the film cast is a long list,
input less than 225 dimensions is fulfilled by padding, CNN has a good ability to capture multi-dimensional features, and use of Max-pooling layer to solve the problem of multi-dimension feature extraction.
\end{itemize}
Finally, these three parts are merged into one layer and then connect to a Softmax layer, and the $L_2$ regularization method is adopted to avoid overfitting.
